%-------------------------
% Resume
% Author : Aditya Patel
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{iftex}

\ifPDFTeX
  \input{glyphtounicode}
  \pdfgentounicode=1
\fi

\usepackage[sfdefault]{roboto} 
\usepackage{fontawesome}

\pagestyle{fancy}
\fancyhf{} 
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-6pt} \scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-7pt}]

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{-8pt}}
\newcommand{\resumeItemListStart}{\begin{itemize}\vspace{-2pt}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-8pt}}

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge Aditya Patel} \\ \vspace{1pt}
    Windsor, ON \\ \vspace{1pt}
     {adityapatel0905@gmail.com} $|$ {226-260-0363} $|$ \href{https://apatel.xyz/}{Website: apatel.xyz} $|$ \href{https://www.linkedin.com/in/aditya-patel52/}{LinkedIn: aditya-patel52}
\end{center}

% %-----------SUMMARY-----------
% \section{Summary}
%   \begin{itemize}[leftmargin=0.15in, label={}]
%     \small{\item{
%       Computer Science student with experience in cloud platforms (Azure, GCP), network automation, and AI/ML. Proficient in Python, Terraform, and Ansible, with a strong background in developing scalable full-stack applications and automating complex infrastructure workflows.
%     }}
%     \vspace{-6pt}
%  \end{itemize}

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, JavaScript, TypeScript, Java, C, C++, SQL, Rust, PHP, MySQL} \\
     \textbf{Tools \& Cloud}{: Azure, Terraform, Ansible, NetBox IPAM, Git, Firebase, GCP, Docker, Supabase, AWS} \\
     \textbf{Frameworks}{: React.js, Node.js, Express, Tailwind, PyTorch, pandas, NumPy, Scikit-learn, Matplotlib}
    }}
    \vspace{-6pt}
 \end{itemize}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Bachelor of Computer Science (Honours)}{Sep. 2023 -- Apr. 2027}
      {University of Windsor}{Windsor, ON}
        \resumeItemListStart
            \resumeItem{Minor in Mathematics}
        \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Network Automation \& Operations Intern}{Jan. 2026 -- Present}
      {Enbridge}{Chatham, ON}
      \resumeItemListStart
        \resumeItem{Currently contributing to enterprise network automation and cloud infrastructure initiatives by developing Python-based scripts and utilizing Azure cloud services.}
        \resumeItem{Managing IP address management (IPAM) and network documentation via NetBox to ensure data integrity.}
        \resumeItem{Collaborating with senior engineers to identify manual bottlenecks and implement automated operational tasks.}
      \resumeItemListEnd

    \resumeSubheading
      {Naval Warfare Officer}{Jan. 2024 -- Present}
      {Royal Canadian Navy}{Windsor, ON}
      \resumeItemListStart
        \resumeItem{Served as Divisional Officer overseeing a cross-functional team of 17 personnel, directing day-to-day operations, welfare, and training while fostering mission effectiveness within the division.}
        \resumeItem{Administered personnel management and training oversight, maintaining qualifications and readiness records.}
      \resumeItemListEnd

    \resumeSubheading
      {Teaching Assistant}{Sep. 2024 -- Dec. 2025}
      {University of Windsor}{Windsor, ON}
      \resumeItemListStart
        \resumeItem{Lead weekly lab sessions to consolidate course content for 70+ students, focusing on data structures and algorithms.}
      \resumeItemListEnd

    \resumeSubheading
      {Software Development Intern}{Jan. 2024 -- Apr. 2024}
      {Glendor, Inc}{Remote}
      \resumeItemListStart
        \resumeItem{Utilized local LLM models to redact personal information in medical documents, achieving 99\% accuracy.}
        \resumeItem{Designed automated scripts in Python to evaluate model performance, reducing manual validation time by 20+ hours, and ensuring robust evaluation across 500+ files.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
    \resumeProjectHeading{\href{https://github.com/Champion2005/reforge}{{\textbf{Reforge}}} $|$ \emph{TypeScript, Zod, Vitest, Vite}}{2026}
      \resumeItemListStart
      \resumeItem{Built \texttt{reforge-ai}, a TypeScript library that repairs malformed LLM JSON, validates/coerces data with Zod, and returns typed results via \texttt{guard()}.}
      \resumeItem{Implemented \texttt{forge()} with automatic retry and provider adapters for OpenAI-compatible APIs (OpenRouter, Groq, Ollama), Anthropic, and Google; designed for Node, Bun, Deno, and Edge runtimes.}
      \resumeItemListEnd

    \resumeProjectHeading{\href{https://github.com/Champion2005/botblocks}{{\textbf{BotBlocks}}} $|$ \emph{React, Three.js, Pyodide, OpenRouter API}}{2026}
      \resumeItemListStart
      \resumeItem{Added an LLM-powered autonomous agent system to a browser robotics simulator, including tool-calling loops for navigation, vision, and motor control.}
      \resumeItem{Built custom tool support, camera controls, and a live AI activity log while keeping the entire simulation setup-free and browser-native.}
      \resumeItemListEnd

    \resumeProjectHeading{\href{https://github.com/Champion2005/amicooked}{{\textbf{amicooked}}} $|$ \emph{React, Firebase, OpenRouter API, GitHub API}}{2026}
            \resumeItemListStart
      \resumeItem{Developed an AI-powered GitHub portfolio auditor that analyzes account signals and generates personalized, actionable career-improvement roadmaps.}
      \resumeItem{Delivered contribution analytics and profile quality insights through an interactive web interface; recognized as a WinHacks 2026 finalist.}
            \resumeItemListEnd

        \resumeProjectHeading{\href{https://github.com/Champion2005/nbpull}{{\textbf{nbpull}}} $|$ \emph{Python, NetBox API, Automation}}{2026}
            \resumeItemListStart
      \resumeItem{Engineered a read-only CLI utility for NetBox IPAM with async HTTP pagination, strict typed models, and safe query workflows for network teams.}
      \resumeItem{Published a packaged tool with rich terminal output and batch query support to reduce manual data pulls and entry errors in operations.}
            \resumeItemListEnd
    \resumeSubHeadingListEnd

\end{document}